Hypertension and microbiome

### 2019-05-27 articletwo.Rmd
Fixing DIAB = 1 bug

```{r maaslin runs, results = 'hide'} 
maaslin <- list()

genus.core.bacteria <- pseq.genus.core %>%
    abundances %>%
    rownames %>%
    replace.brackets %>%
    mygrep(".Bacteria$", .)

maaslin$genus <- maaslinwrapper(pseq = pseq.genus.core,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                           "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = paste0(genus.core.bacteria, collapse = ","))
```

@@

```{r table beta diversity}
adonis.species$max %>%
    data.table::rbindlist(id = "model_name") %>%
    dplyr::filter(term %in% c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION")) %>%
    dplyr::select(response, R2, "Pr(>F)") %>%
    mutate(p.value = pub.p(`Pr(>F)`))
```

@@

>>>>

```{r maaslin runs, results = 'hide'} 
if (!file.exists("rds/maaslin.rds")) {
    maaslin <- list()
    genus.core.bacteria <- pseq.genus.core %>%
        abundances %>%
        rownames %>%
        replace.brackets %>%
        mygrep(".Bacteria$", .)

    pseq.species %>% meta %>% pull(DIAB) %>% summary
    pseq.genus.core %>% meta %>% pull(DIAB) %>% as.factor %>% summary

    maaslin$genus <- maaslinwrapper(pseq = pseq.genus.core,
                                    looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE",
                                               "HYPERTENSION"),
                                    forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X",
                                               "DIAB", "BL_USE_RX_C03",
                                               "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                                    taxa = paste0(genus.core.bacteria, collapse = ","))
    saveRDS(maaslin, file = "rds/maaslin.rds")
} else {
    maaslin <- readRDS("rds/maaslin.rds")
}
```

@@

```{r table beta diversity}
adonis.species$max %>%
    data.table::rbindlist(id = "model_name") %>%
    dplyr::filter(term %in% c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION")) %>%
#    dplyr::select(response, R2, "Pr(>F)") %>%
    mutate(p.value = pub.p(`Pr(>F)`))
```

@@

```{r adonis demo}
data(dune)
data(dune.env)
adonis(dune ~ Management, data=dune.env, permutations=99)$aov.tab
adonis(dune ~ Management, data=dune.env, permutations=99)$coefficients
```

```{r age sex bmi}
lm(MAP ~ BL_AGE + SEX + BMI, data = dset.alpha) %>% summary
```
